---
title: "Lab4"
author: "Balaji Ramkumar and Amish Satish"
date: "15/10/2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is for the creation of a package that can perform line regression. In this assignment the main task is to learn about the classes in R. The code for linear regression is done using the implementation of rc class.

#Setting up the class
```{r, eval=FALSE, include=TRUE}

linreg <-setRefClass ( Class = "linreg",
                      
                      fields = list(formula = "formula",
                                    
                                    data = "data.frame",parsedata = "character",beta="matrix",
                                    
                                    ybar="matrix",ebar="matrix",
                                    
                                    ddf="numeric",sigma_sq="numeric",varian="numeric",stdres="matrix",
                                    
                                    var_beta="matrix",t_beta="matrix",p="matrix"))
```

According to the syntax of Rc classs we need to add certain function that performs certain tasks. These functions are added as a list to the methods.

In this line regression we have 7 functions that are assigned the methods as a list.
```{r, eval=FALSE, include=TRUE}
initialize= function(formula,data){
                          
                          formula  <<- formula
                          
                          data <<- data
                          
                          parsedata <<- deparse(substitute(data))
                          
                          x <- model.matrix(formula, data)
                          
                          yy  <- all.vars(expr = formula)[1]
                          
                          y <- (data[, yy])
                          
                          
                          
                          
                          beta<<-solve(t(x) %*% x) %*% t(x) %*% y
                          
                          ybar<<-x %*% beta
                          
                          ebar<<- y -ybar
                          
                          ddf<<- nrow(x)-ncol(x)
                          
                          sigma_sq<<-as.numeric((t(ebar) %*% ebar) / ddf)
                          
                          var_beta<<-  sigma_sq * solve(t(x) %*% x)
                          
                          varian<<-round(sqrt(sigma_sq), 2)
                          
                          t_beta<<-beta / sqrt(diag(var_beta))
                          
                          p<<-pt(abs(t_beta), ddf,lower.tail=FALSE)
                          
                          stdres<<-sqrt(abs((ebar - mean(ebar)) / sqrt(sigma_sq)))
                          
                        },     
                        
                
                        
                        print = function() {
                          
                          
                          
                          cat("\n","Call:","\n",
                              
                              paste("linreg(", "formula = ", formula[2]," ", formula[1], " ", formula[3],", ", "data = ", parsedata, ")",sep = "", collapse = "\n" ),
                              
                              "\n","Coefficients:","\n",
                              
                              paste(row.names(beta),
                                    
                                    sep = "  ", collapse ="  " ),"\n",
                              
                              format(round(beta,2), justify = "centre",width = 10))
                          
                        },
                        
                        
                        
                        plot=function() {
                          
                          
                          
                          library(ggplot2)
                          
                          library(ggThemeAssist)
                          
                      
                          
                          liu_graphic_theme<-   theme(
                            
                            
                            
                            panel.background = element_rect(fill="white"),
                            
                            plot.margin = unit(c(1,1,1,1), "cm"),
                            
                            plot.caption = element_text(size=12, hjust=0.5, margin=margin(t=15)),
                            
                            plot.title = element_text(color="#666666", face="bold", size="15",hjust=0.5),
                            
                            panel.grid.major.y = element_blank(),
                            
                            panel.grid.minor.y = element_blank(),
                            
                            panel.grid.major.x = element_blank(),
                            
                            panel.grid.minor.x = element_blank(),
                            
                            axis.line = element_line(color= "#666666", size=0.1),
                            
                            axis.text.x = element_text(color="#666666", size="5"),
                            
                            axis.text.y = element_text(color="#666666", size="5"),
                            
                            axis.title.x = element_text(color="#666666", size="12", face="bold"),
                            
                            axis.title.y = element_text(color="#666666", size="12", face="bold"),
                            
                            axis.ticks.x = element_line(color = "blue", size = 0.3)
                            
                          )
                          
                          
                          
                          b<-expression(bold(sqrt(bold("Standardized Residuals"))))
                          
                          caption<-  paste("linreg(", formula[2]," ", formula[1], " ", formula[3], ")")
                        
                          
                          df<- data.frame(FittedValues=ybar,Residulas=ebar)
                          
                          Plot1<-ggplot(df, aes(x = FittedValues, y = Residulas))+
                            
                            geom_point(shape = 21, colour = "#666666", fill = "white", size = 3, stroke = 1.5) + ggtitle("Residual vs Fitted") +
                            
                            geom_abline(slope = 0, intercept = 0,linetype = "dotted") +
                            
                            geom_smooth(method = "loess",color = "red", se = FALSE) +
                            
                            ylab("Residuals") + xlab("Fitted values")+labs(caption=caption)+
                            
                            liu_graphic_theme
                          
                          
                          
                          df1<- data.frame(FittedValues=ybar,Residulas1=stdres)
                          
                                 
                
                          Plot2<-ggplot(df1, aes(x = FittedValues, y = Residulas1))+
                            
                            geom_point(shape = 21, colour = "#666666", fill = "white", size = 3, stroke = 1.5) + ggtitle("Scale-Location") +
                            
                            geom_abline(slope = 0, intercept = 0,linetype = "dotted") +
                            
                            geom_smooth(method = "loess",color = "red", se = FALSE) +ylab(b)+
                            
                            labs(caption=caption)+
                            
                            xlab("Fitted values")+ 
                            
                            liu_graphic_theme
                          
                          
                          
                          return(list("Residual vs Fitted"= Plot1,"Scale Location"= Plot2))
                          
                          
                          
                        },
                        
                        
                        pred =function(){
                          
                          cat("Predicted values or fitted values:","\n")
                          
                          return(as.vector(round(ybar, 2)))
                          
                        },
                        
                        
                        
                        resid = function(){
                          
                          cat("Vector of Residuals:","\n")
                          
                          return(as.vector(round(ebar, 2)))
                          
                        },
                        
                    
                        
                        coef = function() {
                          
                          cat("Regressions coefficients:","\n\n")
                          
                          return(as.vector(round(beta,2)))
                          
                        },
                        
                        
                        
                      
                        
                        summary = function() {
                          
                          output <- data.frame( rname = rownames(beta),
                                                
                                                Estimate =round(beta,2),Std_err = round(sqrt(diag(var_beta)),2),t_value = round(t_beta, 2),
                                                
                                                pr = round(p, 4))
                          
                          output$rname <- as.character(output$rname)
                          
                          row.names(output) <- NULL
                          
                          output <- rbind(c("","Estimate", "Std. Error", "t value", "Pr(>|t|)"), output)
                          
                          
                          
                          for(i in 2:nrow(output)){
                            
                            
                            
                            if(output$pr[i] == 0){
                              
                              output$pr[i] <- "***"
                              
                            } else if(output$pr[i] > 0 & output$pr[i] <= 0.001){
                              
                              output$pr[i] <- "**"
                              
                            } else if(output$pr[i] > 0.001 & output$pr[i] <= 0.01){
                              
                              output$pr[i] <- "*"
                              
                            } else if(output$pr[i] > 0.01 & output$pr[i] <= 0.05){
                              
                              output$pr[i] <- "."
                              
                            } else if(output$pr[i] > 0.05 & output$pr[i] <= 0.1){
                              
                              output$pr[i] <- " "
                              
                            } else if(output$pr[i] > 0.1){
                              
                              output$pr[i] <- " "
                              
                            }
                            
                          }
                          
                          cat("\n Call:\n\n",
                              
                              paste("linreg(", "formula = ", formula[2]," ", formula[1], " ", formula[3],", ", "data = ", parsedata, ")",sep = "", collapse = "\n" ),
                              
                              "\n\n Coefficients:\n\n")
                          
                          
                          
                          for(i in 1:ncol(output)){
                            
                            distance <- max(nchar(as.character(output[, i])), na.rm = TRUE)
                            
                            for(j in 1:nrow(output)){
                              
                              output[j, i] <- format(output[j, i], width=distance,justify = c("right"))
                              
                            }
                            
                          }
                          
                          
                          
                          for(i in 1:nrow(output)){
                            
                            cat(paste(as.character(output[i, ]),collapse = " "),"\n")
                            
                          }
                          
                          cat("\n Residual standard error:",varian, "on", ddf, "degrees of freedom")
                          
                          
                          
                        }))
```

The output is plotted using ggplot as a poinnts with a regression line passing through it.
                      
